Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
done with the title

PCA for 3 factors
```{r}
library(plot3D)

@@

@@

cSYG6_DF <- rplot(corrr_SYG6_DF) +
  ggtitle("Correlation for corrr_SYG6_DF, 2nd phase")

@@

cv_SYG6 <-fviz_pca_var(SYG6_xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), title ="SYG6:2nd")

@@

@@

cSYG1_2DF <- rplot(corrr_SYG1_2DF) +
  ggtitle("Correlation for corrr_SYG1_2DF, 3rd phase")

@@

cv_SYG1_2 <- fviz_pca_var(SYG1_2xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), title ="SYG1_2:3rd")

SYG1_2PC1_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 1, top = 7)
SYG1_2PC2_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 2, top = 7)

@@

@@

cSYG1_1DF <- rplot(corrr_SYG1_1DF) +
  ggtitle("Correlation for corrr_SYG1_1DF, 2nd phase")

@@

cv_SYG1_1 <-fviz_pca_var(SYG1_1xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), title ="SYG1_1:2nd")

SYG1_1PC1_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 1, top = 7)
SYG1_1PC2_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 2, top = 7)

@@

### three sites at once, using corrr
library(patchwork)
cSYG6_DF + cSYG1_2DF + cSYG1_1DF+ plot_layout(ncol=1)

@@

I'm working on how to read oulines and how to use them for anlaysis

>>>>

PCA for 3 factors. We don't think we need this for now. 
```{r}
library(plot3D)

@@

# make n=element number 
count_SYG6 <- length(which(SYG6_df$SPstage.Stage == 2))

@@

cSYG6_DF <- rplot(corrr_SYG6_DF) +
  ggtitle(paste("Correlation SYG6: 2nd Phase", "(n =", count_SYG6,")"))

@@

cv_SYG6 <-fviz_pca_var(SYG6_xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")) +
             ggtitle(paste("SYG6: 2nd Phase", "(n =", count_SYG6,")"))

@@

# make n=element number 
count_SYG1_2 <- length(which(SYG1_2df$SPstage.Stage == 3))

@@

cSYG1_2DF <- rplot(corrr_SYG1_2DF) +
  ggtitle(paste("Correlation SYG1_2: 3rd Phase", "(n =", count_SYG1_2,")"))

@@

cv_SYG1_2 <- fviz_pca_var(SYG1_2xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")) +
  ggtitle(paste("SYG1_2: 3rd Phase", "(n =", count_SYG1_2,")"))

SYG1_2PC1_v <- fviz_contrib(SYG1_2xx_pca, choice = "var", axes = 1, top = 7)
SYG1_2PC2_v <- fviz_contrib(SYG1_2xx_pca, choice = "var", axes = 2, top = 7)

@@

# make n=element number 
count_SYG1_1 <- length(which(SYG1_1df$SPstage.Stage == 2))

@@

cSYG1_1DF <- rplot(corrr_SYG1_1DF) +
  ggtitle(paste("Correlation SYG1_1: 2nd Phase", "(n =", count_SYG1_1,")"))

@@

cv_SYG1_1 <- fviz_pca_var(SYG1_1xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07")) +
            ggtitle(paste("SYG1_1: 2nd Phase", "(n =", count_SYG1_1,")"))

SYG1_1PC1_v <- fviz_contrib(SYG1_1xx_pca, choice = "var", axes = 1, top = 7)
SYG1_1PC2_v <- fviz_contrib(SYG1_1xx_pca, choice = "var", axes = 2, top = 7)

@@

### three sites at once, using corrr
library(patchwork)
cSYG6_DF + cSYG1_2DF + cSYG1_1DF + plot_layout(ncol=1)

@@

I'm working on how to read oulines and how to use them for anlaysis. We may not use this for the research.
